---
title: "SEED Experiment 1"
author: "Morgan Shumaker"
output: github_document
editor_options: 
  chunk_output_type: console
---
```{r}
library(pacman) 
p_load(tidyverse, dplyr, devtools, ggplot2, gplots, skimr, markdown, rmarkdown, broom, ggridges, readxl, BSDA, scales, ggthemes, readr)
```

## Importing Data 
```{r - long}
SEED_Exp1 <- read_xlsx("R_Exp1_SEED.xlsx")
```

```{r - wide}
SEED_Exp1_wide <- read_xlsx("R_Exp1SEED_wide.xlsx")
```

## Errorless
To run a z-test with this package (BSDA), the data needs to be in a data frame
so that R recognizes it as an object:
```{r}
SEED_Exp1_wide <- data.frame(SEED_Exp1_wide)
```

*Create data frames*
```{r}
  Older_Errorless <- data.frame(SEED_Exp1_wide$Older_Errorless)
```

```{r}
  Younger_Errorless <- data.frame(SEED_Exp1_wide$Younger_Errorless)
```

*Z test*
```{r}
  z.test(x = Older_Errorless, y = Younger_Errorless, alternative = "two.sided", mu = 0, sigma.x = 15, sigma.y = 15)
```

## Errorful
*Create data frames*
```{r}
  Older_Errorful <- data.frame(SEED_Exp1_wide$Older_Errorful)
```

```{r}
  Younger_Errorful <- data.frame(SEED_Exp1_wide$Younger_Erroful)
```

*Z test*
```{r}
  z.test(x = Older_Errorful, y = Younger_Errorful, alternative = "two.sided", mu = 0, sigma.x = 15, sigma.y = 15)
```

## Graphics
```{r}
SEED_Plots <- read_xlsx("SEED_Exp1_RPlots.xlsx")
```

*Creating proportion of people who did better in errorful*
```{r}
SEED_errorful <- SEED_Plots %>%
  group_by(AgeGroup) %>%
  count(BetterErrorful)
```

```{r}
rename(SEED_errorful, totaln = n)
```

```{r}
Errorful_Young <- SEED_errorful %>%
  filter(AgeGroup == 1) %>%
  mutate(totaln = (sum(n))) 
```

```{r}
Errorful_Old <- SEED_errorful %>%  
  filter(AgeGroup == 2) %>%
  mutate(totaln = sum(n))
```

```{r}
ErrorfulTotal <- full_join(Errorful_Young, Errorful_Old)
```

```{r}
ErrorfulTotal <- ErrorfulTotal %>% 
  mutate(errorfulprop = n/totaln)
```

*Creating proportion of people who did better in errorless*

```{r}
SEED_errorless <- SEED_Plots %>%
  group_by(AgeGroup) %>%
  count(BetterErrorless)
```

```{r}
rename(SEED_errorless, totaln = n)
```

```{r}
Errorless_Young <- SEED_errorless %>%
  filter(AgeGroup == 1) %>%
  mutate(totaln = (sum(n))) 
```

```{r}
Errorless_Old <- SEED_errorless %>%  
  filter(AgeGroup == 2) %>%
  mutate(totaln = sum(n))
```

```{r}
ErrorlessTotal <- full_join(Errorless_Young, Errorless_Old)
```

```{r}
ErrorlessTotal <- ErrorlessTotal %>% 
  mutate(errorlessprop = n/totaln)
```

*Combining data frames*

```{r}
BetterIn_Total <- full_join(ErrorfulTotal, ErrorlessTotal)
```

## Creating Metacognition Errorless

```{r}
Meta_errorless <- SEED_Plots %>%
  group_by(AgeGroup) %>%
  count(Metacognition)
```

```{r}
rename(Meta_errorless, totaln = n)
```

```{r}
MetaErrorless_Y <- Meta_errorless %>%
  filter(AgeGroup == 1) %>%
  mutate(totaln = (sum(n))) 
```

```{r}
MetaErrorless_O <- Meta_errorless %>%  
  filter(AgeGroup == 2) %>%
  mutate(totaln = sum(n))
```

```{r}
MetaErrorlessTotal <- full_join(MetaErrorless_Y, MetaErrorless_O)
```

```{r}
MetaErrorlessTotal <- MetaErrorlessTotal %>% 
  mutate(metaerrorless_prop = n/totaln)
```

## Creating Metacognition Errorful 

```{r}
Meta_errorful <- SEED_Plots %>%
  group_by(AgeGroup) %>%
  count(Metacognition)
```

```{r}
rename(Meta_errorful, totaln = n)
```

```{r}
MetaErrorful_Y <- Meta_errorful %>%
  filter(AgeGroup == 1) %>%
  mutate(totaln = (sum(n))) 
```

```{r}
MetaErrorful_O <- Meta_errorful %>%  
  filter(AgeGroup == 2) %>%
  mutate(totaln = sum(n))
```

```{r}
MetaErrorfulTotal <- full_join(MetaErrorful_Y, MetaErrorful_O)
```

```{r}
MetaErrorfulTotal <- MetaErrorfulTotal %>% 
  mutate(metaerrorfulprop = n/totaln)
```

```{r}
MetacognitionTotal <- full_join(MetaErrorfulTotal, MetaErrorlessTotal)
```

## Creating Full Data Set 

```{r}
SEEDTotal <- full_join(MetacognitionTotal, BetterIn_Total)
```


```{r}
write_csv(SEEDTotal, path = "/Users/morgan/Desktop/TCU/Hargis Lab/Projects/SEED/Exp 1 Data/SEEDTotal.csv")
```

```{r}
SEED_Graphs <- read_csv("/Users/morgan/Desktop/TCU/Hargis Lab/Projects/SEED/Exp 1 Data/SEEDTotal_Graph.csv")
```


```{r}
SEED_Graphs %>% 
  ggplot(aes(y = PropAcc, x = AgeGroup, fill = Metacognition, position = MetacogProp, warnings = FALSE)) + geom_col() 
```

```{r}
SEED_Graph <- SEED_Graphs %>% 
  mutate(Condition = Metacognition) 
```

```{r}
SEED_Graph %>%   
ggplot(aes(y = PropAcc, x = AgeGroup, fill = Metacognition, position = "stack", warnings = FALSE)) + geom_col() +facet_wrap(~Condition)
```



```{r}

```


ggplot(SEED_Plots, aes(x = Age_Group, fill = Condition)) + geom_bar(position = "stack") +  facet_wrap(~Metacog) +
  scale_y_continuous(labels = scales::percent_format(scale = 1)) +
  labs(x = "Age Group", y = "Percent") + 
  theme_minimal() + theme(panel.border = element_blank(),
          panel.grid.major = element_blank(),
          panel.grid.minor = element_blank()) 

## To change labels on graph
brexit %>%
  count(region, opinion) %>%
  group_by(region) %>%
  mutate(opinion_prop = n / sum(n)) %>%
  ggplot(aes(y = opinion, x = opinion_prop, fill = opinion, warnings = FALSE)) +
  geom_col() +facet_wrap(~region,
    nrow = 1, labeller = label_wrap_gen(width = 12)) +
  labs(
    title = "Was Britain right/wrong to vote to leave EU?",
    subtitle = "YouGov Survey Results, 2-3 September 2019",
    caption = "Source: bit.ly/2lCJZVg",
    x = "Proportion", y = NULL
  ) +
  scale_fill_manual(values = c(
    "Wrong" = "#ef8a62",
    "Right" = "#67a9cf",
    "Don't know" = "gray"
  )) +
  theme_minimal() +
  scale_x_continuous(labels = percent)```{r}
SEED_Plots <- SEED_Plots %>%
  mutate(Metacog = case_when(Metacognition == "0" ~ "Errorless",
                             Metacognition == "1" ~ "Errorful",
                             TRUE ~ as.character(Metacognition)))
```

## Bar Graph 
